### 2016-02-25 ch02-qlogms/excitation-design.tex
Repeat assumption in system part

Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, mechatronics, and vibration testing\TODO{citation (ISMA?)} amongst others.

@@

  The main problem is that network and dynamic signal analyzers typically
  rely on an equidistant frequency grid that comes with the \gls{DFT}.
  A logarithmically spaced signal, on the other hand, does not match well to an equidistant frequency grid.
  More specifically, the lack of frequency resolution at the lowest frequencies hampers the quality of the power distribution at the low edge of the frequency band.
  To circumvent this disadvantage, we will construct quasi-logarithmically spaced signals.
  Their frequency spacing is approximately logarithmic but nevertheless conforms to the DFT's linear frequency grid.

@@

Moreover, the results from \secref{sec:excitation:ex:sumOfSecondOrderSipmle} for the sum of simplified second order systems, i.e. equation \eqref{eq:excitation:sumSys}, extend directly to the generic \gls{LTI} system in \eqref{eq:excitation:PFE} for the second-order sub-systems.
\begin{assumption}
\TODO{assume separation in freq}
\end{assumption}

\begin{assumption}
\TODO{small damping}
\end{assumption}

\begin{remark}
\TODO{leads to block-diagonal information matrix such that the variance of the FRF is decoupled near the resonances}
\end{remark}

>>>>

Such problem settings occur in many diverse fields of experimentation, such as the measurement of biochemical impedances~\citep{Bragos2001,Sanchez2011}, electrochemical impedance spectroscopy~\citep{Niedostatkiewicz2009,VanGheem2004,Breugelmans2010}, electronics~\citep{Munir2011}, vibration analysis and acoustics testing amongst others.
%TODO{ meer referenties? }

@@

  The main problem is that network and dynamic signal analyzers typically
  rely on an equidistant frequency grid that comes with the \gls{DFT}.
  A logarithmically spaced signal, on the other hand, does not match well to an equidistant frequency grid.
  More specifically, the lack of frequency resolution at the lowest frequencies hampers the quality of the power distribution at the low edge of the frequency band.
  To circumvent this disadvantage, we will construct quasi-logarithmically spaced signals.
  Their frequency spacing is approximately logarithmic but nevertheless conforms to the linear frequency grid of the \gls{DFT}.

@@

Moreover, the results from \secref{sec:excitation:ex:sumOfSecondOrderSipmle} for the sum of simplified second order systems, i.e. equation \eqref{eq:excitation:sumSys}, extend directly to the generic \gls{LTI} system in \eqref{eq:excitation:PFE} for the second-order sub-systems under the assumptions given below.

\begin{assumption}
The sub-systems in \eqref{eq:excitation:PFE} all are either lightly damped ($\damping \ll \sqrt{1/2}$) or are not of interest to the user.
\end{assumption}

\begin{assumption}
The resonance frequencies $\wn[i]$ and $\wn[j]$ of all the different sub-systems in \eqref{eq:excitation:PFE} are well-separated in the frequency domain.
\end{assumption}

Under these assumptions, the Fisher information matrix will be approximately a diagonal block matrix, where the $i^{\text{th}}$ block corresponds to the parameters $\left[\wn[i], \wz[i], \damping[i], \dc[i,1], \ldots, \dc[i,M_{2,i}] \right]$ of a particular sub-system.
Using the same logic as in \secref{sec:excitation:ex:sumOfSecondOrderSipmle}, this means that the variance of the complete system is approximately equal to the variance obtained for each sub-system, due to the decoupling of the Fisher information matrix.
